\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-26 paper.tex

 \begin{figure}
\begin{center}
\includegraphics [width=0.75\columnwidth] {fig/testbed.pdf}
\caption{Testbed topology with failure probabilities}
\label{testbed}
\end{center}
\end{figure}
%
%
% \begin{figure}
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/evaluation/testbed-admit.pdf}
%\caption{Admission control comparison.}
%\label{admission-control2}
%\end{center}
%\end{figure}
%
%
%
%\begin{figure}
%\centering
%\subfigure[Availability satisfaction]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
%\subfigure[Admission time]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/testbed-public-2.pdf}}
%\caption{Traffic scheduling comparison.}
%\label{testbed-traffic-scheduling}
%\end{figure}

@@

\begin{figure}
\centering
\subfigure[\mathsf{BATE} v.s. other TE algorithms]{
\includegraphics[width=0.45\textwidth]{fig/evaluation/fixed-shuduling.pdf}}
\subfigure[augmented with \textit{fixed} admission control]{
\includegraphics[width=0.45\textwidth]{fig/evaluation/fixed-scheduling.pdf}}
\caption{Traffic scheduling results under simulations}
\label{scheduling-benefit}
\end{figure}

@@

We then compare the traffic scheduling capability of $\mathsf{BATE}$ against FFC, TEAVAR, SWAN, SMORE and B4.
The methodology is similar to the post-processing simulation in TEAVAR \cite{Teavar}, 
where we simulate different failure scenarios according to their probabilities, 
and in each scenario we record the demands that can be satisfied. 
If the \textit{achieved availibility}, i.e., the total posterior probabilities of \textit{qualified} scenarios where a user's bandwidth target is met, is larger than the user's availability target, 
then the BA demand is \textit{satisfied}. 
We plot the overall percentage of satisfied BA demands under each arrival rate (averaged across all simulations) in Figure \ref{scheduling-benefit}(a). $\mathsf{BATE}$ nearly always achieves a satisfaction ratio around 100\%, with a leading margin of up to 40\%, especially under a high arrival rate. 
This clearly demonstrates $\mathsf{BATE}$'s advantage by matching  stringent availability requirements  
with reliable links.

\iffalse
%We write down the bandwidth loss of each scenario for each demand and each scenario's corresponding probability.
The sum of scenario probability where demand is fully satisfied reflects the \textit{achieved availability}.
%If a demand's , then the availability defined in SLA is \textit{satisfaction}.
The term \textit{satisfaction percentage} refers to the fraction of total arrival demands whose achieved availability are higher than their availability targets throughout duration.
Figure \ref{scheduling-benefit}(a) demonstrates that $\mathsf{BATE}$ can even make up to 40\% more demands satisfy SLA availability.
%Demands SLA violation of  $\mathsf{BATE}$ mainly comes from admission control rejection.
%The reason for this is that $\mathsf{BATE}$ adopts admission control and it considers the diverse availability targets of different bandwidth demands.
$\mathsf{BATE}$ can make demands with stringent availability requirements pass links with high reliability, therefore, their availability targets can be guaranteed, but other schemes are unable differentiate demands.
To show this benefit, we adopt \textit{Fixed} admission control for each traffic scheduling algorithm, then Figure \ref{scheduling-benefit}(b) shows $\mathsf{BATE}$ performs at least 10\% better than other algorithms under the \textit{Fixed} admission control method.

Figure \ref{sim-profit} shows the average monetary gain percentage for the scenario in which one failure could occur in the network.
We can see $\mathsf{BATE}$  is able to retain 30\% more profit than other algorithms when network fails.
\fi

>>>>

 \begin{figure}
\begin{center}
\includegraphics [width=0.8\columnwidth] {fig/testbed.pdf}
\caption{Testbed topology with failure probabilities}
\label{testbed}
\end{center}
\end{figure}
%
%
% \begin{figure}
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/evaluation/testbed-admit.pdf}
%\caption{Admission control comparison.}
%\label{admission-control2}
%\end{center}
%\end{figure}
%
%
%
%\begin{figure}
%\centering
%\subfigure[Availability satisfaction]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
%\subfigure[Admission time]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/testbed-public-2.pdf}}
%\caption{Traffic scheduling comparison.}
%\label{testbed-traffic-scheduling}
%\end{figure}

@@

\begin{figure}
\centering
\subfigure[\mathsf{BATE} v.s. other TE algorithms]{
\includegraphics[width=0.45\textwidth]{fig/evaluation/fixed-scheduling.pdf}}
\subfigure[augmented with \textit{fixed} admission control]{
\includegraphics[width=0.45\textwidth]{fig/evaluation/fixed-shuduling.pdf}}
\caption{BA satisfaction results under simulations}
\label{scheduling-benefit}
\end{figure}

@@

We then compare the traffic scheduling capability of $\mathsf{BATE}$ against FFC, TEAVAR, SWAN, SMORE and B4.
The methodology is similar to the post-processing simulation in TEAVAR \cite{Teavar}, 
where we simulate different failure scenarios according to their probabilities, 
and in each scenario we record the demands that can be satisfied. 
If the \textit{achieved availibility}, i.e., the total posterior probabilities of \textit{qualified} scenarios where a user's bandwidth target is met, is larger than the user's availability target, 
then the BA demand is \textit{satisfied}. 
We plot the overall percentage of satisfied BA demands under each arrival rate (averaged across all simulations) in Figure \ref{scheduling-benefit}(a). $\mathsf{BATE}$ nearly always achieves a satisfaction ratio around 100\%, with a leading margin of at least 20\% under a high arrival rate (rate=6 in the figure). 
To further demonstrates $\mathsf{BATE}$'s advantage in matching stringent availability requirements  
with reliable links, we further augment each TE algorithm with the \textit{fixed} admission control 
scheme. The satisfaction ratios are plotted in Figure \ref{scheduling-benefit}(b), where $\mathsf{BATE}$
still performs at least 10\% better than the others.

\iffalse
%We write down the bandwidth loss of each scenario for each demand and each scenario's corresponding probability.
The sum of scenario probability where demand is fully satisfied reflects the \textit{achieved availability}.
%If a demand's , then the availability defined in SLA is \textit{satisfaction}.
The term \textit{satisfaction percentage} refers to the fraction of total arrival demands whose achieved availability are higher than their availability targets throughout duration.
Figure \ref{scheduling-benefit}(a) demonstrates that $\mathsf{BATE}$ can even make up to 40\% more demands satisfy SLA availability.
%Demands SLA violation of  $\mathsf{BATE}$ mainly comes from admission control rejection.
%The reason for this is that $\mathsf{BATE}$ adopts admission control and it considers the diverse availability targets of different bandwidth demands.
$\mathsf{BATE}$ can make demands with stringent availability requirements pass links with high reliability, therefore, their availability targets can be guaranteed, but other schemes are unable differentiate demands.
To show this benefit, we adopt \textit{Fixed} admission control for each traffic scheduling algorithm, then Figure \ref{scheduling-benefit}(b) shows $\mathsf{BATE}$ performs at least 10\% better than other algorithms under the \textit{Fixed} admission control method.
\fi

Figure \ref{sim-profit} shows the average monetary gain percentage for the scenario in which one failure could occur in the network.
We can see $\mathsf{BATE}$  is able to retain 30\% more profit than other algorithms when network fails.
